---
title: "p8105_hw3_nja2140"
Author: Naina Ahuja
Assignment: Homework 3
output: github_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(p8105.datasets)
library(ggridges)
```

Problem 1: Instacart Data. Load the data from the p8105.datasets. Write a short description of the dataset, noting the size and structure of the data, describing some key variables, and giving illustrative examples of observations
```{r}
data("instacart") 
instacart
```
The size of the dataset `Instacart` is `r nrow(instacart)` observtaions and `r ncol(instacart)` variables. Key variables include all associated details of the order and the product acquired. The mean hour of day where orders were made is `r mean(pull(instacart, order_hour_of_day))`. Te median number of days between orders is `r median(pull(instacart, days_since_prior_order))`

Answer the following (commenting on the results of each):
  -How many aisles are there, and which aisles are the most items ordered from?

  -Make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered. Arrange aisles sensibly, and organize your plot so others can read it.

  -Make a table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”. Include the number of times each item is ordered in your table.
  
-Make a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week; format this table for human readers (i.e. produce a 2 x 7 table)

```{r}
instacart_one=instacart %>%
  janitor::clean_names() %>%
  group_by(aisle_id, aisle) %>%
  summarize(n = n()) %>%
  arrange(desc(n))
instacart_one
```
There are 134 aisles. Aisle 83, 24, 123 and 120 are where the most items were ordered from. 

```{r}
aisle_scatter=
  filter(instacart_one, n> 10000)
  ggplot(aisle_scatter, aes(x = reorder(aisle, -n), y =n)) +
  geom_point(color = "turquoise") +
  theme(
    axis.text.x = element_text(angle = 90, hjust = 1), 
    axis.text = element_text(size = 7.5)) +
  labs(
    title = "Number of items ordered in each aisle",
    x = "Aisle",
    y = "Number of products"
  )
```

```{r}
insta_table=instacart %>%
  filter(aisle == "baking ingredients" | 
         aisle == "dog food care" | 
         aisle == "packaged vegetables fruits") %>%
  group_by(aisle, product_name) %>%
  summarize(n = n()) %>%
  top_n(3) %>%
  arrange(desc(n)) %>%
  knitr::kable ()
insta_table
```

```{r}
insta_table2=instacart %>%
  filter(product_name == "Pink Lady Apples" | 
         product_name == "Coffee Ice Cream") %>%
  group_by(product_name, order_dow) %>%
  summarize(mean_order_hour= mean(order_hour_of_day)) %>%
  select(product_name, order_dow, mean_order_hour) %>%
  pivot_wider(
    names_from = order_dow,
    values_from = mean_order_hour
  ) %>%
  knitr::kable ()
insta_table2
```

Problem 2: Load the BRFSS data. First, do some data cleaning:
-Format the data to use appropriate variable names;
-Focus on the “Overall Health” topic
-Include only responses from “Excellent” to “Poor”
-Organize responses as a factor taking levels ordered from “Poor” to “Excellent”

```{r}
data("brfss_smart2010")
brfss_smart2010

brfss_new=brfss_smart2010 %>%
  janitor::clean_names() %>%
  filter(topic == "Overall Health", 
         response == "Excellent" | 
         response == "Very good" | 
         response == "Good"| 
         response == "Fair"|
         response == "Poor") %>%
  mutate(response = factor(response, labels = c("Poor","Fair","Good","Very good", "Excellent" ))) %>%
  select(-location_id, -data_value_footnote_symbol, -data_value_footnote)
brfss_new
```
-In 2002, which states were observed at 7 or more locations? What about in 2010?
-Construct a dataset that is limited to Excellent responses, and contains, year, state, and a variable that averages the data_value across locations within a state. Make a “spaghetti” plot of this average value over time within a state (that is, make a plot showing a line for each state across years – the geom_line geometry and group aesthetic will help).
-Make a two-panel plot showing, for the years 2006, and 2010, distribution of data_value for responses (“Poor” to “Excellent”) among locations in NY State

```{r}
brfss_new %>%
  filter(year == "2002") %>%
  group_by(locationabbr) %>%
  summarize(
    n_locations = n_distinct(geo_location)) %>%
  filter(n_locations>6) %>%
  arrange(desc(n_locations)) 
```
The states that were observed at 7 or more locations in 2002 are PA, MA, NJ, CT, FL, NC.

```{r}
brfss_new %>%
  filter(year == "2010") %>%
  group_by(locationabbr) %>%
  summarize(
    n_locations = n_distinct(geo_location)) %>%
  filter(n_locations>6) %>%
  arrange(desc(n_locations)) 
```
The states that were observed at 7 or more locations in 2010 are FL, NJ, TX, CA, MD, NC, NE, WA, MA, NY, OH, CO, PA, SC.



